\section{User Guide}

The website is currently hosted on a developmental server, while the database is hosted on a local machine.
The website can be accessed at \url{http://127.0.0.1:5000/} only when the local server is running.

\subsection*{Navigation through the application}

The front-end of the application is inspired from top online retailers in the real-market.
The user interface is designed to be as smooth and intuitive as possible.
Key principles like \Acomment{Consistency}, \Acomment{Accessibility}, and \Acomment{Keep it simple, stupid} were kept in mind while creating the UI.

Although there remain some minor bugs and unimplemented features, the application is fully functional and can be used by all stakeholders.

\begin{stakeholder}[Store Managers (Admins)]
    Creating an admin account is possible only through the intervention of the developers.
    An admin must log in to their panel by clicking on the \texttt{Log in as Admin} button shown in the footer.
    The admin dashboard holds the power to manage the entire business, from each individual product to the entire supply chain.
    Using the dashboard, the admin gets access to aggregates such as trends in orders, best-selling products, demographics, etc.
\end{stakeholder}

\begin{stakeholder}[Customers]
    To use EBMS to its full potential, a customer must create an account using the \texttt{Log In} button located in the naviagation bar.
    From there, the \texttt{Create an account} button can be used to create an account.

    After logging in, the customer can select products to add to their cart through the catalogue.
    The customer can also write reviews for the products that they have purchased.
    They can also add balance to their EBMS wallet, which can be used to pay for orders.
    They can view their personal information, their order history, and the current active (undelivered) orders on their profile page,
    which can be accessed through the \texttt{Account} button on the navigation bar.
\end{stakeholder}

\begin{stakeholder}[Suppliers]
    Suppliers can create an account following similar steps as mentioned above.

    The supplier dashboard allows the supplier to view their products.
    They can add new products, update existing products, and delete products from their dashboard.
    Suppliers also get access to the reviews and ratings of their products.
    They can view and edit their personal information such as their warehouse address thorugh the \texttt{Account} button.
    EBMS also generates sales reports for the supplier, which can be accessed (and possibly in the future, downloaded) from the dashboard.
\end{stakeholder}

\begin{stakeholder}[Delivery Agents]
    Delivery agents must also create an account to use EBMS.

    Delivery agents can find their active orders on their dashboard.
    From there, they can mark orders as delivered.
    They are also allowed access to their previous orders, and the details of each order, if required.
    They can also view and edit their personal information such as their contact number through the \texttt{Account} button.
    Delivery agents have ratings and reviews associated with them, which can also be viewed on their dashboard.
\end{stakeholder}