\section{Abstract}

Electronics has always been a booming industry.
With the advent of the internet, the industry has seen a massive shift towards online retail.
However, it is difficult to keep track of the technical requirements of a store and keep all stakeholders involved and updated.

This is where we come in with \textbf{EBMS}, the \textbf{ElectroBase Management System}.
EBMS is an online retail platform for electronics.
It aims to provide a common platform for customers, suppliers, store managers, and delivery agents.
\begin{itemize}
    \item
    It is an easy solution for the \textbf{customers}, as it aims to provide a diverse catalogue of products to customers.
    The customers get to choose from a wide range of categories, make changes to their cart, and make secure payments with a method of their choice.
    \item
    The \textbf{suppliers} get to keep track of their products and edit their description, price, etc. as and when required.
    The application also manages and generates their sales statistics.
    \item
    The database/store managers (\textbf{admins}) get assisted in monitoring the transactions and managing the inventory.
    Based on the requirements, they can add deals or combos on the available products or remove categories from their store.
    \item
    EBMS provides a platform for \textbf{delivery agents} to manage all orders that have been assigned to them.
    They can toggle their activity status and view the feedback given to them.
\end{itemize}

The primary focus of the project is to design an efficient back-end.
We aim to create a system that is smooth and easy to use for the customers and easy to manage for the suppliers.
The system should support efficient searching through the catalogue and should be able to handle a large number of transactions.

\divider

The aim of this project is to bring to life an integrated online retail store for electronics.
The project will bring all stakeholders on a common platform and will ensure a smooth
and easy-to-use experience for the customers.

Through our project, we attempt to model a real-world problem and provide a solution.
Hence, this full-stack project will involve usage of various technologies and tools to create a robust and efficient system.
This involves usage of the \textbf{Flask Micro-Framework (Python-3)} for front-end development and \textbf{MySQL} for back-end development.