\deadline{5}{Embedded SQL Queries, OLAP Queries, and Triggers}{March 26, 2023}

\section*{\Huge Frontend Development}
\vspace*{10pt}

Since this deadline now requires embedding SQL queries in a host programming language, the frontend development has also been started.
As decided previously, the host langauge is Python-3, and the frontend is being developed using the Flask Web-Development Micro Framework. \\
The raw frontend is in the first stages of development and is hosted on a local server.
This document contains references and bibliographies for all open-source code available on the internet for tasks like placing sortable tables on a page,
CSS animations, and JavaScript functions for form validation.

\section*{\Huge Embedded SQL Queries}
\vspace*{10pt}

As of now, the only SQL queries which have been embedded in the Python code are those for which the frontend interaces have been developed.
In the future, these will be refactored into small \texttt{.sql} files and imported into the Python code for security\footnote{
    The embedded SQL Queries are currently not protected against SQL Injection Attacks.
} and readability purposes.
\vspace*{10pt} \\
The following is a (non-exhaustive) list of already embedded SQL queries:

\begin{enumerate}
    \item \input{./SQL/Embedded/query-01.tex}
    \item \input{./SQL/Embedded/query-02.tex}
    \item \input{./SQL/Embedded/query-03.tex}
    \item \input{./SQL/Embedded/query-04.tex}
    \item \input{./SQL/Embedded/query-05.tex}
    \item \input{./SQL/Embedded/query-06.tex}
    \item \input{./SQL/Embedded/query-07.tex}
    \item \input{./SQL/Embedded/query-08.tex}
    \item \input{./SQL/Embedded/query-09.tex}
    \item \input{./SQL/Embedded/query-10.tex}
    \item \input{./SQL/Embedded/query-11.tex}
    \item \input{./SQL/Embedded/query-12.tex}
\end{enumerate}

\section*{\Huge OLAP SQL Queries}
\vspace*{10pt}

OLAP queries are (mainly) utilised by the Admin in our use case to perform data analytics.
The OLAP data is separated from the rolled-up form before rendering the HTML page. These queries are also embedded in Python.
\vspace*{10pt} \\
The following is a (non-exhaustive) list of already implemented OLAP SQL queries:

\begin{enumerate}
    \item \input{./SQL/OLAP/query-01.tex}
    \item \input{./SQL/OLAP/query-02.tex}
    \item \input{./SQL/OLAP/query-03.tex}
    \item \input{./SQL/OLAP/query-04.tex}
    \item \input{./SQL/OLAP/query-05.tex}
\end{enumerate}

\section*{\Huge Triggers}

The following triggers are identified according to the use cases and implemented in the database:

\begin{enumerate}
    \item \input{./SQL/Triggers/trigger-01.tex}
    \item \input{./SQL/Triggers/trigger-02.tex}
    \item \input{./SQL/Triggers/trigger-03.tex}
\end{enumerate}

\vfill \pagebreak